\documentclass[a4wide,10pt]{extarticle}
\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}
\setlist{noitemsep}
\usepackage{color}
\usepackage{array}
\usepackage{hyperref}
\usepackage[compact]{titlesec}
\titlespacing*{\section}{0pt}{6pt}{6pt}
\titlespacing*{\subsection}{0pt}{6pt}{6pt}

\begin{document}
\thispagestyle{empty}

\sffamily{

\begin{center}
\textbf{Real World Project - Meeting 03.03}
\vspace{0.33cm}
\end{center}

\begin{center}
\begin{tabular}{| m{2.8cm} | m{13.6cm} |} \hline
\textbf{Date and Time} & March 10th\\ \hline
\textbf{Participants} & \\ \hline
\textbf{Apologies} & \\ \hline
\end{tabular}
\end{center}


\begin{center}
{\large \textbf{Outcomes to achieve\\}}
\begin{itemize}
    \item Samathy to report on MongoDB encryption
    \item Abdul to report on progress generating data
    \item Oliver + Paul to report on progress with RSA Encryption algorithm
    \item Start development of system - Discuss tasks
\item \textbf{To identify stories to be completed in first sprint.}
\item To assign team members to complete tasks
\end{itemize}
\end{center}

\begin{center}
{\large{\textbf{Actions from previous meeting:}}}
\begin{itemize}
    \item Samathy to research MongoDB inbuilt encryption
    \item Abdul to attempt to simulate location data
    \item Oliver + Paul to continue implimenting RSA Encryption system.
    \end{itemize}
\end{center}


\subsection*{Agenda}
{\large \textbf{Report on MongoDB encryption (S.B)\\}}
Present and discuss findings regarding MongoDB's inbuilt encription systems.
\hfill \break
\textit{Unfortunatly MongoDB only offers encryption to Enterprise customers only. This is out of the budget of this project.
As such, Samathy proposes to impliment our own encryption of the data in the database, and log the other full DB encryption methods that could be used in a commercial enviroment.
Such as: 
\begin{itemize}
    \item Linux Full disk Encryption
    \item File system encryption
\end{itemize}}
\hfill \break
\textbf{Actions:\\}
\hfill \break
\hfill \break
\hfill \break
\hfill \break

{\large \textbf{Present development on producing simulated location data (A\\}} 
\textbf{Actions:\\}
\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break

{\large \textbf{Report on progress implimenting RSA encryption (O.K, Paul)\\}}
\textit {Maybe if this is implimented, the next stage would be to make it into a re-packageable Python module for use throughout the system.\\}
\color{red}{Important:} Additionally, this code should be in the Github organizeation by now. \\
\textbf{Actions:\\}
\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break

{\large \textbf{Next stage of this project\\}}
\textit{The next stage of this project really is implimenting the thing. Where are we going to start, and what are we going to begin with?\\}
\textbf{Actions:\\}
\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break

{\large \textbf{Any Other Business?\\}}
\begin{itemize}
    \item \color{red}{Reminder of timeframes\\}
\end{itemize}
\textbf{Actions:\\}
\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break

{\large \textbf{Action Items:\\}}
\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break



\subsection*{\color{red}{Next Meeting: Thursday March 17th}}

}

\end{document}
