\documentclass[a4wide,10pt]{extarticle}
\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}
\setlist{noitemsep}
\usepackage{color}
\usepackage{array}
\usepackage{hyperref}
\usepackage[compact]{titlesec}
\titlespacing*{\section}{0pt}{6pt}{6pt}
\titlespacing*{\subsection}{0pt}{6pt}{6pt}

\begin{document}
\thispagestyle{empty}

\sffamily{

\begin{center}
\textbf{Real World Project - Meeting 25.02}
\vspace{0.33cm}
\end{center}

\begin{center}
\begin{tabular}{| m{2.8cm} | m{13.6cm} |} \hline
\textbf{Date and Time} & February 25th.h \\ \hline
\textbf{Participants} & \\ \hline
\textbf{Apologies} & \\ \hline
\end{tabular}
\end{center}


\begin{center}
{\large \textbf{Outcomes to achieve\\}}
\begin{itemize}
\item To discuss data researched by Ben
\item Discuss multi-level data anonymity strategy.
\item Discuss Dewan's idea to rank anthrax symptoms.
\item To discuss generated user stories.
\item To identify stories to be completed in first sprint.
\item To assign team members to complete tasks
\end{itemize}
\end{center}

\begin{center}
{\large{\textbf{Actions from previous meeting:}}}
\begin{itemize}
\item Existing data to be researched by Ben R due to lack of a report presented by Abena.\\
\item Both Olivers to implement multi-level anonymity of data strategy as well as example programs implementing RSA encryption and generation of anonymous data.\\
\item Requirements Capture and generation of user stories to be done by Samathy, Dewan and Abdul.\\
\item Dewan to research SCRUM for personal learning.\\
\item Dewan, Samathy and Abdul to generate short, precise user stories for Monday. As well as ranking them in order of importance.\\
\item Dewan to start working o 'decision tables' ranking anthrax symptoms. If time permits.\\


    \end{itemize}
\end{center}


\subsection*{Agenda}
{\large \textbf{Progress on data researched and generated (B.R)\\}}
Present and discuss data researched by Ben.
\textbf{Actions:\\}
EE Data? - No chance of getting this data as this data is expensive and only really avalible to large organiseations.
Gov.UK Have lots of data sets

Formats:
\begin{itemize}
    \item JSON
    \item CSV
\end{itemize}


JSON decided on due to compatability with MongoDB

\hfill \break
\hfill \break
{\large \textbf{Progress on Multi-Level data anonymity design and test implementation (O.K, O.R)\\}}
Present progress on data anonymity and security.
\textbf{Actions:\\}
Test program implimented - To advance program to impliment RSA encryption of data and RSA encryption of data during transfer.
\hfill \break
\hfill \break
{\large \textbf{Discuss symptom ranking idea (D.A)\\}}
\textbf{Actions:\\}
Dewan not present - Abena generated her own scheme to rank symptoms and will finish this scheme and post it.
\hfill \break
\hfill \break
{\large \textbf{Discuss requirements Identified (S.B, D.A, A.M)\\}}
Present identified requirements.
\textbf{Actions:\\}
\hfill \break
\hfill \break
\hfill \break
\hfill \break
{\large \textbf{Identify requirements to be achieved by next meeting.\\}}
\textbf{Actions:\\}
\hfill \break
\hfill \break
\hfill \break
\hfill \break
{\large \textbf{Items to be carried over to next meeting\\}}
\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break
{\large \textbf{Any Other Business?\\}}
\textbf{Actions:\\}
\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break

{\large \textbf{Action Items:\\}}
(A)Olivers + Paul to work out how to encrypt data and send data between systems.
(A)Samathy to generate symptom data.
(A)Samathy to set up a MongoDB server.
\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break



\subsection*{\color{red}{Next Meeting: Thursday March 3rd}}

}

\end{document}
