\documentclass[a4wide,10pt]{extarticle}
\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}
\setlist{noitemsep}
\usepackage{color}
\usepackage{array}
\usepackage{hyperref}
\usepackage[compact]{titlesec}
\titlespacing*{\section}{0pt}{6pt}{6pt}
\titlespacing*{\subsection}{0pt}{6pt}{6pt}

\begin{document}
\thispagestyle{empty}

\sffamily{

\begin{center}
\textbf{Real World Project - Meeting 18.02}
\vspace{0.33cm}
\end{center}

\begin{center}
\begin{tabular}{| m{2.8cm} | m{13.6cm} |} \hline
\textbf{Date and Time} & February 18th \\ \hline
\textbf{Participants} & Samathy, Ben, Oliver, Oliver, Abdul, Dewan\\ \hline
\textbf{Apologies} & \\ \hline
\end{tabular}
\end{center}


\begin{center}
{\large \textbf{Outcomes to achieve\\}}
\begin{itemize}
\item To present reports generated last week.
\item To discuss appropriate tools for the tasks at hand.
\item To generate initial ideas of the project structure.
\item To generate user stories.
\item To identify stories to be completed in first sprint.
\item To assign team members to complete tasks
\end{itemize}
\end{center}

\subsection*{Agenda}
{\large \textbf{Progress on Projects\\}}
Progress to be reported on any other work completed.\\
\textbf{Actions:\\}
No progress reported\\
{\large \textbf{Present FOSS Tools and Languages Report\\}}
Present report on FOSS data processing tools and programming languages.\\
\textbf{Actions:\\}
Samathy researched statistical processing languages Python and R. Python choose as everyone already knows the language.\\
Database solutions presented. None selected due to lack of data.\\
{\large \textbf{Present Security Report\\}}
Present report on Annonomising data, Securing Big data in holding and transit.\\
\textbf{Actions:\\}
Presented Data Protection act and ideas for storing and sending data safely using encryption methods.\\
Man in the middle attacks considered, in addition to physical security.\\
(A) Both Olivers to implement multi-level annonimising of data strategy as well as example programs implementing RSA encryption and generation of anonymised data.\\
{\large \textbf{Present Data Reports\\}}
Present reports on existing datasets and platforms.Report on the structure of datasets.\\
\textbf{Actions:\\}
(A) This task to be completed by Ben R due to lack of a report presented by Abena.\\
{\large \textbf{Present past projects research\\}}
Present report on past projects of a similar ilk.\\
\textbf{Actions:\\}
Projects researched include IBM, CDC and EpiSimDemics. Projects identified as worth reading about to get an idea of who this kind of thing works and how we can implement it ourselves.\\
{\large \textbf{Generate user stories for entire project\\}}
Capture individual features, requirements and sections of the project. \\ 
Split these requirements into achievable sections.\\
\textbf{Actions:\\}
(A)Requirements Capture and generation of user stories to be done by Samathy, Dewan and Abdul.\\
{\large \textbf{Identify project's structure and interfaces in key areas\\}}
Look at all the elements of the project and attempt to identify how these parts will communicate with each other.\\
Discuss module interface design.\\
\textbf{Actions:\\}
Not discussed
\hfill \break
{\large \textbf{Identify user stories to be actioned this sprint.\\}}
\textbf{Actions:\\}
Not discussed
\hfill \break
{\large \textbf{Identify team members to take sprint elements forward\\}}
\textbf{Actions:\\}
Not discussed
\hfill \break
{\large \textbf{Any Other Business?\\}}
\textbf{Actions:\\}
Not discussed
\hfill \break
{\large \textbf{Items to be carried forward to next meeting\\}}
\textbf{Actions:\\}
Dewan to research SCRUM for personal learning.\\
Dewan, Samathy and Abdul to generate short, precise user stories for monday. As well as ranking them in order of importance.\\
Dewan to start working o 'decision tables' ranking anthrax symptoms. If time permits.\\

\hfill \break
\hfill \break

{\large \textbf{Action Items:\\}}
(A) Existing data to be researched by Ben R due to lack of a report presented by Abena.\\
(A) Both Olivers to impliment multi-level annonimising of data stratagy as well as example programs implimenting RSA encryption and generation of anonymised data.\\
(A) Requirements Capture and generation of user stories to be done by Samathy, Dewan and Abdul.\\
(A) Dewan to research SCRUM for personal learning.\\
(A) Dewan, Samathy and Abdul to generate short, precise user stories for monday. As well as ranking them in order of importance.\\
(A) Dewan to start working o 'decision tables' ranking anthrax symptoms. If time permits.\\



\subsection*{\color{red}{Next Meeting:Thursday Febuary 25th 2016}}

}

\end{document}
