\documentclass[a4wide,10pt]{extarticle}
\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}
\setlist{noitemsep}
\usepackage{color}
\usepackage{array}
\usepackage{hyperref}
\usepackage[compact]{titlesec}
\titlespacing*{\section}{0pt}{6pt}{6pt}
\titlespacing*{\subsection}{0pt}{6pt}{6pt}

\begin{document}
\thispagestyle{empty}

\sffamily{

\begin{center}
\textbf{Real World Project - Meeting 03.03}
\vspace{0.33cm}
\end{center}

\begin{center}
\begin{tabular}{| m{2.8cm} | m{13.6cm} |} \hline
\textbf{Date and Time} & March 3rd \\ \hline
\textbf{Participants} & \\ \hline
\textbf{Apologies} & \\ \hline
\end{tabular}
\end{center}


\begin{center}
{\large \textbf{Outcomes to achieve\\}}
\begin{itemize}
\item To discuss data researched by Ben.
\item Samathy to present project architecture ideas.
\item Discuss project architecture ideas.
\item Discuss secutity hotpoints.
\item Discuss project progress.
\item Discuss timeframes.
\item \textbf{To identify stories to be completed in first sprint.}
\item To assign team members to complete tasks
\end{itemize}
\end{center}

\begin{center}
{\large{\textbf{Actions from previous meeting:}}}
\begin{itemize}
\item Olivers + Paul to work out how to encrypt data and send data between systems.
\item Samathy to generate symptom data.
\item Samathy to set up a MongoDB server.
    \end{itemize}
\end{center}


\subsection*{Agenda}
{\large \textbf{Progress on data researched and generated (B.R)\\}}
Present and discuss data researched by Ben.
\textbf{Actions:\\}

Project architecture approved.
Formal documentation required.\\
\hfill \break
\hfill \break
\hfill \break
\hfill \break
{\large \textbf{Present project architecture idea. (S.B)\\}}
Present ideas geerated for possible project structure.
\textbf{Actions:\\}
\hfill \break
\hfill \break
\hfill \break
\hfill \break
{\large \textbf{Discuss project structure ideas\\}}
\textbf{Actions:\\}
\hfill \break
\hfill \break
{\large \textbf{Discuss security hotpoints\\}}
Identify security hotpoints in design\\
\textbf{Actions:\\}
Hotpoints include between the client and server.\\
RSA Encryption to be used here\\
Additionally, Database needs to be encrypted. \\
Samathy to reasearch MongoDB built in encryption.\\
\hfill \break
\hfill \break
\hfill \break
\hfill \break
{\large \textbf{Discuss timeframes\\}}
\textbf{Actions:\\}
\hfill \break
\hfill \break
\hfill \break
\hfill \break
{\large \textbf{Identify requirements to be achieved by next meeting.\\}}
\textbf{Actions:\\}
\hfill \break
\hfill \break
\hfill \break
\hfill \break
{\large \textbf{Items to be carried over to next meeting\\}}
\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break
{\large \textbf{Any Other Business?\\}}
\textbf{Actions:\\}
\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break

{\large \textbf{Action Items:\\}}
Abdul to attempt to simulate location data.\\
Oliver and Paul to continue making progress on RSA encryption system.\\
\hfill \break
\hfill \break
\hfill \break
\hfill \break
\hfill \break



\subsection*{\color{red}{Next Meeting: Thursday March 10th}}

}

\end{document}
